---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
```{r include=FALSE}
knitr::opts_chunk$set(echo=TRUE)

options(scipen = 1, digits = 2)
```


## Loading and preprocessing the data
```{r}
unzip(zipfile = "./activity.zip")
fb<-read.csv("./activity.csv")
```



## What is mean total number of steps taken per day?
```{r}
cb<-aggregate(steps~date,fb,sum)
mx<-mean(cb$steps)
md<-median(cb$steps)
hist(cb$steps, 
       main="Total Number of Steps", 
       xlab="Steps"
     )

```

The mean of total steps per day is `r mx`.  
The median of same is `r md`.


## What is the average daily activity pattern?
```{r}
zb<-aggregate(steps~interval,fb,mean)

plot(zb$interval,zb$steps,
     type = "l", 
     main="Average Steps by Interval, Oct to Nov 2012",
     ylab = "Average of Steps Taken", 
     xlab = "Interval")
```

The 5-minute interval that on average contains the most number of steps is:  

```{r}
zb[which.max(zb$steps),][1]
```

## Imputing missing values
There are a total of `r sum(is.na(fb$steps))` missing values in the dataset, i.e. NA. To impute values to those rows, we will follow a plan of find-match-replace:  
1. Find a row that needs to be imputed, e.g. when row\$steps == NA;  
2. Match the interval of that row to the interval in a data frame with average steps by interval, e.g. zb\$interval == row\$interval;  
3. Replace the missing value with the average value for that interval  
```{r}
for(i in 1:nrow(fb)){
  if(is.na(fb$steps[i])){
    fb$steps[i]<-zb$steps[zb$interval==fb$interval[i]]
  }
}

nb <- data.frame(fb)

mxx<-mean(nb$steps)
mdd<-median(nb$steps)
hist(nb$steps, 
       main="Total Number of Steps", 
       xlab="Steps"
     )
```



## Are there differences in activity patterns between weekdays and weekends?
```{r}
wknds<-c("Saturday","Sunday")

nb$weekf<-ifelse(weekdays(as.Date(as.character(nb$date))) %in% wknds, 
                 'weekend', 
                 'weekday')

nb$weekf<-factor(nb$weekf)

nbm<-aggregate(nb$steps,list(nb$interval,nb$weekf),mean)
colnames(nbm)<-c("interval","wday","steps")

require(ggplot2)
ggplot(nbm, aes(interval, steps, colour = factor(wday))) +
  geom_line() + facet_wrap(~ wday, ncol = 2, scales = "free") +
  guides(colour = "none") +
  theme() 
  


```

